---
title: "p8105_hw1_xl3494"
output: html_document
---

# Problem 1

```{r}
library("moderndive")
library(tidyverse)
data("early_january_weather")
```

The early_january_weather dataset contains hourly meteorological data for LGA, JFK and EWR for the month of January 2013. The data frame has 358 rows and 15 columns. Variables include origin (weather station), year, month, day, hour (time of recording), temp, dewp (temperature and dewpoint in F), humid (relative humidity), wind_dir, wind_speed, wind_gust (wind direction in degrees, speed and gust speed in mph), precip (precipitation in inches), pressure (sea level pressure in millibars), visib (visibility in miles), and time_hour (date and hour of recording). The mean temperature is 39.6 F.

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color = humid)) +geom_point() +
labs(
title = "Temperature over Time",
x = "Time",
y = "Temperature (F)",
color = "Humidity (%)"
)
```
The scatter plot shows an increase in temperature over the two weeks. Humidity tends to be higher at low temperature and lower at high temperature.
```{r}
ggsave("scatter_plot.pdf", height=4, width=6)
```

# Problem 2
```{r}
df=tibble(
  numberic_vec = rnorm(10),
  logical_vec = rnorm (10)>0,
  char_vec = letters [1:10],
  factor_vec = factor(rep(c("level1", "level2", "level3"), length.out = 10))
)
df

mean(pull(df,numberic_vec))     #ok

mean(pull(df, logical_vec))     #ok

mean(pull(df, char_vec))        #error

mean(pull(df, factor_vec))      #error
```
as.numeric(pull(df,logical_vec)

as.numeric(pull(df,char_vec)

as.numeric(pull(df,factor_vec)

When logical variables are converted to numeric, TRUE = 1, and FALSE = 0. The mean of a logical vector thus gives the proportion of TRUE values.

When character variables are converted to numeric, R gives warning becasue charactors are names and cannot be meaniingfully turned into numbers. So, mean cannot be computed.

When factor variables are converted to numeric, R gives the integers assigned to each level. The numbers don't mean anything and not statistically meaningful, so mean cannot be computed.

